---
title       : Predicting MPG 
subtitle    : Prediction of MPG (Miles/(US) gallon) for different cars
author      : ASK-DataScience
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Introduction

Here, we are trying to predict the MPG (Miles/(US) gallon) for differenct cars using:
  
  
1. Transmission type (0 = Automatic, 1 = Manual)
2. Number of cylinders (4, 6, or 8)
3. Gross horsepower
4. Weight (lb/1000)

--- .class #id 

## Dataset

- mtcars data set was used in this analysis.

```{r}
data(mtcars)
head(mtcars)
mtcars$am <- factor(mtcars$am)
```

--- .class #id 

## Regression Model

- Linear regression model was used. 
- The model includes the relationship between mpg (outcome) and transmission type, number of cylinders, gross horsepower. and weight (regressors).

```{r}
modelFit <- lm(mpg ~ am+cyl+hp+wt, mtcars)
modelFit
```

--- .class #id 

## Prediction

- The user can enter his values for the regressors to get the predicted MPG value.
- This is done using the `predict` function.

```{r, eval=FALSE}
p <- predict(modelFit, newdata = test)
```










